\documentclass[kulak]{tplt} 
% options: kulak (default) or kul

\title{Algebraic Methods in Combinatorics}
\author{Assignment 3}
\date{Summer semester 2022 -- 2023}
\address{
	\textbf{Max Planck Institute for the Mathematics in the Sciences} \\
	\textbf{Universit\"at Leipzig}}


\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbold}
\usepackage{listings}
\usepackage{lineno}
%\usepackage[margin=3cm]{geometry}
\usepackage[all,cmtip, color,matrix,arrow]{xy}
%\usepackage{amsaddr}
\usepackage{tikz-cd}
\usepackage{amsmath}%To use \text 
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[capitalize]{cleveref}
\crefname{thm}{Theorem}{Theorems}
%\usepackage{bbold}
\usepackage[export]{adjustbox}
\usepackage{todonotes}
\usepackage{bm}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{mathtools}
\usepackage{aliascnt}
\newaliascnt{eqfloat}{equation}
\newfloat{eqfloat}{h}{eqflts}
\floatname{eqfloat}{Equation}
\usepackage{dirtytalk}
\usepackage[mathscr]{euscript}


%\def\shuffle{\sqcup\mathchoice{\mkern-7mu}{\mkern-7mu}{\mkern-3.2mu}{\mkern-3.8mu}\sqcup\,}
\newcommand{\qshuffle}{\overline{\shuffle}}


\theoremstyle{definition}
\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lm}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{obs}[thm]{Observation}
\newtheorem{defin}[thm]{Definition}
\newtheorem{smpl}[thm]{Example}
\newtheorem{quest}[thm]{Question}
\newtheorem{exe}[thm]{Exercise}
\newtheorem{const}[thm]{Construction}
\newtheorem{prob}[thm]{Problem}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{rem}[thm]{Remark}
\crefname{lm}{Lemma}{Lemmas}
\crefname{thm}{Theorem}{Theorems}
\crefname{prop}{Proposition}{Propositions}
\crefname{defin}{Definition}{Definitions}
\crefname{rem}{Remark}{Remarks}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\PP}{\mathbb{P}}

\newcommand{\one}{\mathbb{1}}

\newcommand{\CC}{\mathcal C}
\newcommand{\JJ}{\mathcal J}
\newcommand{\II}{\mathcal I}
\newcommand{\BB}{\mathcal B}
\newcommand{\FF}{\mathcal F}

%vectors
\newcommand{\vv}{\mathsf{v}}
\newcommand{\vw}{\mathsf{w}}
\newcommand{\vj}{\mathsf{j}}
\newcommand{\vx}{\mathsf{x}}
\newcommand{\vy}{\mathsf{y}}
\newcommand{\va}{\mathsf{a}}

\newcommand{\spn}{\mathrm{span}}
\newcommand{\rk}{\mathrm{rk}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\maxcut}{\mathrm{maxcut}}
\newcommand{\we}{\mathrm{we}}


\begin{document}

\maketitle
\begin{enumerate}
\item 

\begin{enumerate}
\item  Let $P$ be a $\{1\}$-distance set in $\R^d$, that is any two distinct points $\vx, \vy \in P $ have $||\vx - \vy || = 1$.
Show that $|P| \leq d+1$.
Hint: Use polynomials to show that $|P|\leq d+2$, then fix the proof by adding one polynomial.

\item Let $P$ be a $\{\delta_1, \delta_2\}$ distance set in $\R^d $, and assume that $\delta_1> 2 \delta_2 > 0$.
Show that $|P| \leq d+1$.
Hint: Show that points at distance $\delta_2$ of each other form cliques, then show that a collection of polynomials of degree two is linearly independent.


\item
Let $D $ be a finite set of positive real numbers with $|D| = t$ elements.
Let $P$ be a $D$-distance set in $\R^d$.
Show that $|P| \leq \binom{d+t}{t}$.

\end{enumerate}

\item Let $S$ be a finite set in $\R^d$.
An $S$-simplex is a convex hull of $d+1$ distinct points in $S$.

Fix an integer $d$.
Prove that there is a polynomial $p(x)$ with leading term $c x^{d+1}$, with $c > 0$, such that for any finite set $S$ in $\R^d$ there exists a point $\va \in \R^d$ contained in at least $p(|S|)$ $S$-simplices.

Hint: Use Tveberg's theorem for $r$ as large as possible to find a special point $\va$.
What does the colourful Caratheodory theorem tells us about $\va$?


\item Let $X$ be a finite set in $\R^2$ such that any three points in $X$ can be covered by a closed unit disc.
Show that there is a closed unit disk covering the whole set $X$.
Hint: Three points can be covered by a unit disk if and only if three particular unit disks have non-empty intersection.


\item 
Let $d\geq 1$ be an integer, $I$ a set (possibly infinite) and $\mathcal F \subset \binom{I}{d}$ a finite family with $m\coloneqq |\FF | \geq d+1$.
Assume that any subcollection of $d+1$ sets in $\FF $ intersect, that is for $F_0, \ldots, F_d \in \FF $ we have $\bigcap_{i=0}^d F_i \neq \emptyset$.
Show that 
$$ \bigcap_{F \in \FF} F \neq \emptyset \, . $$
Hint: 
Follow along the proof of Helly's theorem.

\item 
Fix $d, m, r\geq 1$ integers.
Let $\FF = \{ F_0, \ldots, F_m\}$ be a collection of subsets of $[d]$, and assume that $m \geq (d+1)(r-1)$.
Then there are subsets $I_1, \ldots , I_r$ of $\{0, \ldots, m\}$, pairwise disjoint, such that for any $i, j$ in $\{1, \ldots, r \}$ we have
$$ \bigcup_{k \in I_i} F_k = \bigcup_{k \in I_j} F_k , \quad \quad \quad \bigcap_{k \in I_i} F_k = \bigcap_{k \in I_j} F_k \, .$$

Hint: Follow along the proof of Tveberg's theorem.

\end{enumerate}
\end{document}
